Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/paper.tex
fix fig exts & figref

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            Normals & With cube edges & Flat (no shading) \\
            \hline
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge.jpg} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat.jpg} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge.jpg} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat.jpg} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat-edge.jpg} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat.jpg} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat-edge.jpg} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat.jpg} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon, then on an
        octaflower as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=4.5$, while
        our normal estimator are computed using a deviation of $\sigma=4$, and so
        a radius of $r=2\sigma=8$}
        \label{fig:normals-estimation}
    \end{figure}

@@

    \RefFigure{fig-curvatures} displays the results of CNC curvature
    estimations on the digitization of a piecewise smooth shape
    ``Talking D20'', taken from
    \href{https://ten-thousand-models.appspot.com/detail.html?file_id=1533028}{Thingi10K}.
    We compare the differences obtained by just changing the discrete
    normal estimator (available in the \textsc{DGtal} library):
    (column II normals) Integral Invariant normals with $r=6$, (column
    CTriv normals) convolved trivial normals with $r=6$, (column
    Visibility normals) our proposed estimator (VN) with $\sigma=4$ and
    maximal visibility distance $2\sigma$. These parameters were
    chosen so that the respective computation windows of the different
    estimators are approximately the same.

>>>>

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            Normals & With cube edges & Flat (no shading) \\
            \hline
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat-edge} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat-edge} &
            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon, then on an
        octaflower as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=4.5$, while
        our normal estimator are computed using a deviation of $\sigma=4$, and so
        a radius of $r=2\sigma=8$}
        \label{fig:normals-estimation}
    \end{figure}

@@

    Figure~\ref{fig:fig-curvatures} displays the results of CNC curvature
    estimations on the digitization of a piecewise smooth shape
    ``Talking D20'', taken from
    \href{https://ten-thousand-models.appspot.com/detail.html?file_id=1533028}{Thingi10K}.
    We compare the differences obtained by just changing the discrete
    normal estimator (available in the \textsc{DGtal} library):
    (column II normals) Integral Invariant normals with $r=6$, (column
    CTriv normals) convolved trivial normals with $r=6$, (column
    Visibility normals) our proposed estimator (VN) with $\sigma=4$ and
    maximal visibility distance $2\sigma$. These parameters were
    chosen so that the respective computation windows of the different
    estimators are approximately the same.
